Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-10 paper/main.tex
subsection on the angular momentum

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo major axis and the first (third)
  eigenvector.\label{fig:shape_alignment}} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig3.pdf}
\caption{Median of $|\cos\theta|$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) for two different
  grid resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.\label{fig:spin_alignment}} 
\end{figure*}

We now take a look at the alignment of the angularwith the cosmic
web. This characterization is done in terms of the angle between the
angular momentum vector and the first/third eigenvector.

Figure \ref{fig:spin_alignment} shows the results as a function of
the halo mass. In the case of the V-web the trends can be summarized
as follows. Low mass halos $10^{12}$\hMsun do not show any
preferential alignment with the cosmic web. Halos more massive than
this threshold have their spin slightly perpendicular to the
direction defined by the first eigenvector (defining sheets) and
uncorrelated to the third eigenvector (filament direction). This
translates into a weak tendency for the spin to lie on the
sheet-plane.

In the case of the T-web there is a similar trend for low mass halos
$10^{12}$\hMsun not to have any preferential direction with respect to
the cosmic web. High mass halos present a weak alignment with the
first eigen vector and anti-alignment with the third
eigenvector. Summarizing, the spin of massive halos tends to be
slightly perpendicular to filaments and sheets.

@@

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig4.pdf}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and a halo's peculiar
  velocity.} 
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo major axis and the first (third)
  eigenvector.\label{fig:shape_alignment}} 
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig3.pdf}
\caption{Median of $|\cos\theta|$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) for two different
  grid resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.\label{fig:spin_alignment}} 
\end{figure*}

We now take a look at the angular momentum alignment. Figure
\ref{fig:spin_alignment} shows the results as a function of halo mass
following the same panel distributio as in Figure
\ref{fig:shape_alignment}. In all cases we see that these alignment
trends are weaker than shape alignments. For the Vweb low mass halos
$<10^{12}$\hMsun do not show any preferential alignment with the
cosmic web. Halos more massive than this threshold have their angular
momentum slightly perpendicular to the direction defined by the first
eigenvector and uncorrelated to the third eigenvector. This translates
into a weak tendency for the angular momentum to lie parallel to walls.

In the case of the Tweb, the alignment for low mass halos $<10^{12}$\hMsun 
is also absent. More massive halos present a weak alignment along
first eigen vector and anti-alignment with the third eigenvector. This
provides a quantitative expression of the results derived from the
preferential alignment whereby the angular momentum is weakly
perpendicular to filaments.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig4.pdf}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and a halo's peculiar
  velocity.} 
\end{figure*}
